%
% Author: Christopher Bellingham
%
% Minute of meeting.
%

% ====== DOC PREAMBLE ======
\documentclass[a4paper, 12pt]{article}

% Package dependancies.
\usepackage{../latex_common/mom}

% Document attributes.
\title{Minutes of Meeting \\ MSc IT+ Masters Team Project}
\date{}


% ====== DOC TEXT ======
\begin{document}
	\maketitle
	% Date, Location, Author, Participants, Apologies.
	\momtoptable
	{Wed 10-Jan 2018 (Week 1)}
	{Boyd Orr}
	{Christopher Bellingham}
	{Ioannis Athanasiadis [IA]\newline
	Christopher Bellingham [CB]\newline
	Joseph Doogan [JD]\newline
	Pavlos Evangelidis [PE]\newline
	Torquil MacLeod [TM]}
	{-}

	\begin{momitems}
		% Item, Details, Resp., Due.
		\momitem
		{1}
		{Initial discussions took place for Team Organisation Document, specifically the Communication, Information Management, and Tools sections. It was agreed that Slack will be used as primary means of communication. A GitHub repo will store all project information, including code and project documentation. Trello will be used for team visibility of milestones and as a tool for brainstorming requirements and user stories. A regular weekly meeting will be held in the Boyd Orr at 10:00 every Wednesday as a general catch up. Agenda TBC.}
		{INFO}
		{INFO}
		\momitem
		{2}
		{Ref [1], set up Slack workspace.}
		{JD}
		{COMPLETE}
		\momitem
		{3}
		{Ref [1], set up GitHub repo.}
		{CB}
		{COMPLETE}
		\momitem
		{4}
		{Ref [1], set up Trello boards.}
		{JD}
		{COMPLETE}
		\momitem
		{5}
		{Locate template files on Moodle and make initial commit to GitHub.}
		{CB}
		{COMPLETE}
		\momitem
		{6}
		{Team agree that discussion on Roles and Responsibilities and Authority sections should be deferred until everyone has reviewed the assignment specification. Team will meet in Boyd Orr Lab @ 12:00, Fri 12-Jan to discuss and finalise these aspects.}
		{ALL}
		{Fri 12-Jan}
		\momitem
		{7}
		{Ref [6], individually review Assignment Specification and consider desired role(s).}
		{ALL}
		{Fri 12-Jan}
		\momitem
		{8}
		{Per the Suggested Timeline presented in the kick-off lecture, Requirements Gathering and Planning are to be completed within Week 2 (next week). Week 2's weekly meeting (17-Jan) will be used to agree all requirements and the project plan.}
		{INFO}
		{INFO}
		\momitem
		{9}
		{Ref [8], populate Trello with project requirements prior to Week 2's weekly meeting.}
		{ALL}
		{Wed 17-Jan}
	\end{momitems}
\end{document}
