\newpage
\section{Planning \& Review Report}

This section records outcomes from key planning and review meetings.

\subsection{Sprint Planning Meeting (Wed 17-Jan 2018)}

Prior to this meeting, the team collaborated via Trello and Slack to generate user stories.
The purpose of the meeting was to review the stories, remove duplicates, and to establish individual story durations.
In terms of priorities, each story was initially defined as a Must Have, since all generated stories were strictly limited to the requirements of the specification.
The team reserved the right to de-prioritise individual stories should the workload be considered too high.

The team split up the user stories into two main categories, stories related to command line mode; and stories related to online mode.
Durations were allocated for each story. Breakdown was as follows:


\begin{center}
	\begin{tabular}{*{2}c}
		\hline
		\textbf{User Story} & \textbf{Story Points} \\
		\hline
		S0010 & 1 \\
		S0020 & 2 \\
		S0030 & 1 \\
		S0040 & 1 \\
		S0050 & 1 \\
		S0130 & 1 \\
		S0180 & 2 \\
		\hline
		\textbf{Total} & 9 \\
		\hline
	\end{tabular}
	\captionof{table}{Command Line Mode User Stories.}
	\label{table:planning_command_line_stories}
\end{center}
\todo[inline]{Crosscheck story point values with those in User Stories section.}

\begin{center}
	\begin{tabular}{*{2}c}
		\hline
		\textbf{User Story} & \textbf{Story Points} \\
		\hline
		S0190 & 1 \\
		S0200 & 1 \\
		S0210 & 1 \\
		S0220 & 1 \\
		S0230 & 1 \\
		S0240 & 1 \\
		S0250 & 1 \\
		\hline
		\textbf{Total} & 7 \\
		\hline
	\end{tabular}
	\captionof{table}{Online Mode User Stories.}
	\label{table:planning_online_stories}
\end{center}
\todo[inline]{Crosscheck story point values with those in User Stories section.}

\todo{Confirm value.}9 story points was felt to be a reasonable first estimation of the team's available capacity, as such this value was taken as the anticipated velocity for Sprint 1, the scope of which was limited to Command Line mode only.

As such, the scope of Sprint \#1 was chosen to correspond with the stories defined in Table \ref{table:planning_command_line_stories}. Stories within Table \ref{table:planning_online_stories} were tentatively scheduled to be tackled in Sprint \#2.

Since development of all stories appeared feasible, no de-prioritisation of stories was thought necessary upon conclusion of the meeting.


\subsection{Design Meeting (Wed 17-Jan 2018)}


\subsection{Sprint Review/Retrospective Meeting (Wed 24-Jan 2018)}


\subsection{Design Meeting (Wed 24-Jan 2018)}


\subsection{Sprint Retrospective Meeting (Wed 31-Jan 2018)}

Moved to Wed 7-Feb 2018.
