%
% Team organisation document.
%

% ====== DOC PREAMBLE ======
\documentclass[a4paper, 12pt, titlepage]{article}

% Package dependancies.
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref} % Required for hyperlinks
\usepackage{graphicx} % Required for \rot (text rotation on table headers)
\usepackage{pifont} % Required for \ding{51} (tick mark)

% Custom commands.
\newcommand{\rot}{\rotatebox{90}}
\newcommand{\y}{\ding{51}}

% Document attributes.
\title{\textbf{Team Organisation Document} \\ MSc IT+ Masters Team Project}
\author{
    Ioannis Athanasiadis [2057536a] \\
    Christopher Bellingham [2320989b] \\
    Joseph Doogan [2342934d] \\
    Pavlos Evangelidis [2349102e] \\
    Torquil MacLeod [2349654m]
}


\begin{document}

    \maketitle

    \section{Roles and Responsibilities}
    \begin{center}
        \begin{tabular}{r*{5}c}
            & \rot{Ioannis Athanasiadis} & \rot{Christopher Bellingham} 
            & \rot{Joseph Doogan} & \rot{Pavlos Evangelidis} & \rot{Torquil MacLeod} \\
            \hline
            %                                             IA   CB   JD   PE   TM
            Product Owner                               &    &    &    & \y &    \\
            Scrum Master                                &    & \y &    &    &    \\
            Backend Developer (Java)                    & \y & \y & \y & \y & \y \\
            Backend Developer (SQL)                     & \y &    & \y & \y & \y \\
            Frontend Developer (HTML/CSS)               & \y &    & \y &    & \y \\
            Frontend Developer (JavaScript)             & \y &    & \y & \y &    \\
            API Tech Specialist (Dropwizard)            &    &    &    &    & \y \\
            Template Tech Specialist (FreeMarker)       &    &    &    &    & \y \\
            Build Tech Specialist (Maven)               &    & \y & \y & \y &    \\
            Doc Tech Specialist (LaTeX)                 & \y & \y &    & \y &    \\
            UX Analyst                                  &    &    & \y &    & \y \\
            Tester                                      & \y &    & \y &    &    \\
            End User                                    &    &    &    & \y &    \\
            \hline
        \end{tabular}
    \end{center}


    \section{Authority}
    \begin{itemize}
        \item In general, the team will be self-organising and will meet according to the schedule listed in Section \ref{communication}.
        \item Product Owner takes authority for defining priority for each user story.
        \item Technical/operational decisions will be taken by team consensus. Deadlocks will be broken by the Scrum Master.
    \end{itemize}


    \section{Communication} \label{communication}
    \begin{itemize}
        \item Day-to-day:
        \begin{itemize}
            \item Slack [\url{https://thefamousfivegroup.slack.com}]
            \begin{itemize}
                \item Forum for general discussion; development activity summary (via GitHub commit hook); progress summary (via Trello hook); issues; clarifications.
            \end{itemize}
        \end{itemize}
        \begin{itemize}
            \item Informal, opportunistic discussions.
            \begin{itemize}
                \item Naturally between courses, team members share same course selection. Any valuable discussions will be posted to Slack to ensure visibility for all.
            \end{itemize}
        \end{itemize}

        \item Sprint Planning Meeting: (Wed 17-Jan 10:00-12:00, Library Level 5, Room 5C).
        \begin{itemize}
                \item Finalise all user stories; Prioritise all user stories; Select user stories for Sprint 1.
        \end{itemize}

        \item Design Meeting: (Wed 17-Jan 12:00-13:00, Boyd Orr 1024).
        \begin{itemize}
                \item Agree upon class structure; Allocate user stories to team members.
        \end{itemize}

        \item Sprint Review/Retrospective: (Wed 24-Jan 10:00-12:00, Location TBC).
        \begin{itemize}
                \item Summary of completed user stories; Lessons learned; Select user stories for Sprint 2.
        \end{itemize}

        \item Design Meeting: (Wed 24-Jan 12:00-13:00, Boyd Orr 1024).
        \begin{itemize}
                \item Agree technical approach; Allocate user stories to team members.
        \end{itemize}

        \item Sprint Retrospective: (Wed 31-Jan 10:00-12:00, Location TBC).
        \begin{itemize}
                \item Summary of completed user stories; Lessons learned.
        \end{itemize}

        \item Documentation Meeting: (Wed 31-Jan 12:00-13:00, Boyd Orr 1024).
        \begin{itemize}
                \item Review report requirements; allocate tasks to team members.
        \end{itemize}

        \item Ad-hoc meetings (in-person):
        \begin{itemize}
            \item Called as needed, if an issue is raised which cannot be solved via Slack or by an immediate weekly meeting.
        \end{itemize}
    \end{itemize}


    \section{Information Management}
    \begin{itemize}
        \item Code and controlled project documentation:
        \begin{itemize}
            \item GitHub [\url{https://github.com/2320989B/top-trumps}]
        \end{itemize}

        \item Team visibility of milestones, user stories and allocated tasks:
        \begin{itemize}
            \item Trello [\url{https://trello.com/thefamousfive2}]
        \end{itemize}
    \end{itemize}


    \section{Tools}
    \begin{itemize}
        \item As above (GitHub; Trello; Slack).
        \item Core technologies: Java; FreeMarker; Dropwizard; PostgreSQL; HTML: CSS; JavaScript.
        \item Development tools: Eclipse/IntelliJ; Maven.
        \item Project documentation: LaTeX.
    \end{itemize}

\end{document}